---
title: "Mental Health in Tech Survey - Part 1"
author: "Oscar Monroy"
date: "5/19/2022"
output:
  pdf_document: default
  word_document: default
---

```
Timestamp

Age

Gender

Country

state: If you live in the United States, which state or territory do you live in?

self_employed: Are you self-employed?

family_history: Do you have a family history of mental illness?

treatment: Have you sought treatment for a mental health condition?

work_interfere: If you have a mental health condition, do you feel that it interferes with your work?

no_employees: How many employees does your company or organization have?

remote_work: Do you work remotely (outside of an office) at least 50% of the time?

tech_company: Is your employer primarily a tech company/organization?

benefits: Does your employer provide mental health benefits?

care_options: Do you know the options for mental health care your employer provides?

wellness_program: Has your employer ever discussed mental health as part of an 
employee wellness program?

seek_help: Does your employer provide resources to learn more about mental health 
issues and how to seek help?

anonymity: Is your anonymity protected if you choose to take advantage of mental 
health or substance abuse treatment resources?

leave: How easy is it for you to take medical leave for a mental health condition?

mentalhealthconsequence: Do you think that discussing a mental health issue with 
your employer would have negative consequences?

physhealthconsequence: Do you think that discussing a physical health issue with 
your employer would have negative consequences?

coworkers: Would you be willing to discuss a mental health issue with your coworkers?

supervisor: Would you be willing to discuss a mental health issue with your direct supervisor(s)?

mentalhealthinterview: Would you bring up a mental health issue with a potential employer 
in an interview?

physhealthinterview: Would you bring up a physical health issue with a potential employer 
in an interview?

mentalvsphysical: Do you feel that your employer takes mental health as seriously as p. health?

obs_consequence: Have you heard of or observed negative consequences for coworkers with 
mental health conditions in your workplace?
```

```{r}
mht <- read.csv("survey.csv")
summary(mht) # The data seems to be mostly error free, except Gender and age
table(mht$Gender) # There's a lot of misspellings here...

# Normally, I'd do some regex to change the misspelled levels into
# correctly spelled form, but using the indices for the levels would 
# make this job a lot faster. I'll also be making an "Other" level
# to fit all the people who don't fit within the definition of
# cis-gendered. Also because there is a very small smaple size for them.
# Trans women will also be fit into the "Female" category as they choose
# to identify as female. Ultimately, there will be some subjectivity at
# play here; for example, "male leaning androgynous" will be fit in the 
# "Male" category as they still identify as male, but "something kinda male?"
# will be put in the "other" category as they are unsure of their status.
levels(mht$Gender)[c(1,2,3,4,10,20,21,22,38,39,40,42,43,44,45)] <- "Other"
levels(mht$Gender)[c(2,3,7:15,32:35)] <- "Female"
levels(mht$Gender)[-c(1,2)] <- "Male"
table(mht$Gender) # Much better

# Time to fix the age variable.
t10 <- sort(mht$Age)
head(t10, 10) # These are some VERY young people...
tail(t10, 10) # We also got some aged 329 years old and 100 billion years old. Seems normal
error_num <- c(t10[c(1:6, length(t10) - 1, length(t10))])
mht <- mht[-which(mht$Age %in% error_num), ]
summary(mht$Age)

# Now we look for duplicates
sum(duplicated(mht)) # None, luckily
```

# The Demographic

```{r, message=F}
library(ggplot2)
library(dplyr)
# Age groups defined here: 
# https://www.pewresearch.org/fact-tank/2019/01/17/where-millennials-end-and-generation-z-begins/
# Millenial -> 1981-1996 
# Generation X -> 1965-1980 
# Boomer & Silent Gen. -> 1928-1964

gen_groups <- cut(mht$Age, c(17,34,50,75),
                  labels=c("Millenial", "Generation X", "Boomer/Silent Gen"))
mht2 <- cbind(mht, "Gen" = gen_groups)

hist(mht2$Age, col = "Red", xlab = "Age", main = "Histogram of Age Variable",
     ylim = c(0, 150), xlim = c(10, 80), breaks = 20)

a_m <- mht2 %>%
  filter(Gender == "Male")
a_f <- mht2 %>%
  filter(Gender == "Female")
a_o <- mht2 %>%
  filter(Gender == "Other")

hist(a_m$Age, col = rgb(1,0,1,1/4), xlab = "Age", main = "Histogram of Age by Gender",
     ylim = c(0, 125), xlim = c(10, 80), breaks = 20)
hist(a_f$Age, col = rgb(0,1,0,1/4), breaks = 20, add = T)
hist(a_o$Age, col = rgb(0,1,1,1/4), breaks = 20, add = T)
legend(70, 100, legend = c("Male", "Female", "Other"),
       fill = c(rgb(1,0,1,1/4), rgb(0,1,0,1/4), rgb(0,1,1,1/4)))

# We see that the majority of people that answered the survey
# are in their late 20's (25-29).

ggplot(mht2, aes(x = Gender)) +  
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "purple") +
  ylab("Proportion (%)") +
  ggtitle("Proportion of Workers by Gender")
prop.table(table(mht2$Age))

ggplot(mht2, aes(x = Gen)) +  
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "green") +
  ylab("Proportion (%)") +
  ggtitle("Proportion of Workers by Generation")
prop.table(table(mht2$Gen))

p <- prop.table(table(mht2$Gen, mht2$Gender))
p_df <- as.data.frame(p)
p_df

ggplot(p_df, aes(x = Var1, y = Freq, fill = Var2)) + 
  geom_bar(stat="identity", position = "dodge") +
  xlab("Generation") +
  ylab("Proportion (%)") +
  ggtitle("Proportional Frequency of Each Generation by Gender")

fh_gen <- mht2 %>%
  select(Gen, family_history) %>%
  group_by(Gen) %>%
  count(family_history)

ggplot(fh_gen, aes(x = Gen, y = n, fill = family_history)) + 
  geom_bar(stat="identity", position = "dodge") +
  xlab("Generation") +
  ylab("Total") +
  ggtitle("Reported Family History of Mental Illness by Age Group")

table(mht2$Country) # Countries that people from this survey are in
table(mht2$state) # US states that people from this survey are in
```

# Survey REsults

### MH = Mental Health
### PH + Physical Health

```{r, message=F}
library(ggpubr)
summary(mht2[, -c(1:5, 27)])

se <- mht2 %>%
  count(self_employed)

g1 <- ggplot(se[-3, ], aes(x = self_employed, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Reported as Self-Employed") + 
  theme(plot.title = element_text(size = 10))

fh <- mht2 %>%
  count(family_history)

g2 <- ggplot(fh, aes(x = family_history, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Family History of Mental Illness?") + 
  theme(plot.title = element_text(size = 10))

tr <- mht2 %>%
  count(treatment)

g3 <- ggplot(tr, aes(x = treatment, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Sought Treatment for Mental Health?") + 
  theme(plot.title = element_text(size = 10))

wi <- mht2 %>%
  count(work_interfere)
wi2 <- wi[-5, ]
wi2 <- wi2[c(1, 3, 4, 2), ]
wi2$work_interfere <- factor(wi2$work_interfere, levels = wi2$work_interfere)

g4 <- ggplot(wi2, aes(x = work_interfere, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = 1:4) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Mental Health Interferes w/ Work?") + 
  theme(plot.title = element_text(size = 10))

ne <- mht2 %>%
  count(no_employees)
ne2 <- ne[c(1, 5, 3, 2, 4, 6), ]
ne2$no_employees <- factor(ne2$no_employees, levels = ne2$no_employees)

g5 <- ggplot(ne2, aes(x = no_employees, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = 1:6) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("How Many Employees in the Company?") + 
  theme(plot.title = element_text(size = 20))

rw <- mht2 %>%
  count(remote_work)

g6 <- ggplot(rw, aes(x = remote_work, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Work Remotely?") + 
  theme(plot.title = element_text(size = 10))

tc <- mht2 %>%
  count(tech_company)

g7 <- ggplot(tc, aes(x = tech_company, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Work for a Tech Company?") + 
  theme(plot.title = element_text(size = 10))

bn <- mht2 %>%
  count(benefits)

g8 <- ggplot(bn, aes(x = benefits, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Employer Provide MH Benefits?") + 
  theme(plot.title = element_text(size = 10))

co <- mht2 %>%
  count(care_options)

g9 <- ggplot(co, aes(x = care_options, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "purple", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Knowledge of MH Care Employer Have") + 
  theme(plot.title = element_text(size = 10))

wp <- mht2 %>%
  count(wellness_program)

g10 <- ggplot(wp, aes(x = wellness_program, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("MH Part of Employee Wellness Program?") + 
  theme(plot.title = element_text(size = 10))

sh <- mht2 %>%
  count(seek_help)

g11 <- ggplot(sh, aes(x = seek_help, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Resources Provided for MH Issues?") + 
  theme(plot.title = element_text(size = 10))

an <- mht2 %>%
  count(anonymity)

g12 <- ggplot(an, aes(x = anonymity, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Anonymity Kept for MH Issues?") + 
  theme(plot.title = element_text(size = 10))

lv <- mht2 %>%
  count(leave)
lv2 <- lv[c(4, 2, 1, 3, 5), ]
lv2$leave <- factor(lv2$leave, levels = lv2$leave)

g13 <- ggplot(lv2, aes(x = leave, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = 1:5) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Ease of Taking Leave for MH Issues?") + 
  theme(plot.title = element_text(size = 20))

mc <- mht2 %>%
  count(mental_health_consequence)

g14 <- ggplot(mc, aes(x = mental_health_consequence, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Discussing MH Issues have Consequences?") + 
  theme(plot.title = element_text(size = 10))

pc <- mht2 %>%
  count(phys_health_consequence)

g15 <- ggplot(pc, aes(x = phys_health_consequence, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Discussing PH Issues have Consequences?") + 
  theme(plot.title = element_text(size = 10))

cw <- mht2 %>%
  count(coworkers)

g16 <- ggplot(cw, aes(x = coworkers, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "purple", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Willing to Discuss MH Issues w/ Coworkers?") + 
  theme(plot.title = element_text(size = 10))

su <- mht2 %>%
  count(supervisor)

g17 <- ggplot(su, aes(x = supervisor, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "purple", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Willing to Discuss MH Issues w/ Supervisor(s)?") + 
  theme(plot.title = element_text(size = 9))

mi <- mht2 %>%
  count(mental_health_interview)

g18 <- ggplot(mi, aes(x = mental_health_interview, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Willing to Bring Up MH Issues in an Interview?") + 
  theme(plot.title = element_text(size = 9))

pi <- mht2 %>%
  count(phys_health_interview)

g19 <- ggplot(pi, aes(x = phys_health_interview, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Willing to Bring Up PH Issues in an Interview?") + 
  theme(plot.title = element_text(size = 10))

mp <- mht2 %>%
  count(mental_vs_physical)

g20 <- ggplot(mp, aes(x = mental_vs_physical, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("purple", "red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Feel that Employer Takes MH as Seriously as PH?") + 
  theme(plot.title = element_text(size = 8.5))

oc <- mht2 %>%
  count(obs_consequence)

g21 <- ggplot(oc, aes(x = obs_consequence, y = n)) + 
  geom_bar(stat="identity", position = "dodge", fill = c("red", "green")) +
  xlab("Answer") +
  ylab("Total") +
  ggtitle("Heard/Observed Consequences for Coworkers w/ MH Issues?") + 
  theme(plot.title = element_text(size = 10))

g_all <- c(g1, g2, g3, g4, g5, g6, g7,
           g8, g9, g10, g11, g12, g13, g14,
           g15, g16, g17, g18, g19, g20, g21)
ggarrange(g1, g2, g3, g4, g6, g7,
           g8, g9, g10, g11, g12, g14, g15,
            g16, g17, g18, g19, g20, g21, ncol = 2, nrow = 2)
g5
g13
```

# Does Gender Make a Difference in the Survey Answers?

### Since the "other" category of the Gender variable only has a sample
### size of 15, we won't include it as the amount is too small to analyze.

```{r, message = F}
library(rcompanion)
f1 <- table("Gender" = mht2$Gender, "self_employed" = mht2$self_employed)

f2 <- table("Gender" = mht2$Gender, "family_history" = mht2$family_history)

f3 <- table("Gender" = mht2$Gender, "treatment" = mht2$treatment)

f4 <- table("Gender" = mht2$Gender, "work_interfere" = mht2$work_interfere)

f5 <- table("Gender" = mht2$Gender, "no_employees" = mht2$no_employees)

f6 <- table("Gender" = mht2$Gender, "remote_work" = mht2$remote_work)

f7 <- table("Gender" = mht2$Gender, "tech_company" = mht2$tech_company)

f8 <- table("Gender" = mht2$Gender, "benefits" = mht2$benefits)

f9 <- table("Gender" = mht2$Gender, "care_options" = mht2$care_options)

f10 <- table("Gender" = mht2$Gender, "wellness_program" = mht2$wellness_program)

f11 <- table("Gender" = mht2$Gender, "seek_help" = mht2$seek_help)

f12 <- table("Gender" = mht2$Gender, "anonymity" = mht2$anonymity)

f13 <- table("Gender" = mht2$Gender, "leave" = mht2$leave)

f14 <- table("Gender" = mht2$Gender, "mh_consequence" = mht2$mental_health_consequence)

f15 <- table("Gender" = mht2$Gender, "ph_consequence" = mht2$phys_health_consequence)

f16 <- table("Gender" = mht2$Gender, "coworkers" = mht2$coworkers)

f17 <- table("Gender" = mht2$Gender, "supervisor" = mht2$supervisor)

f18 <- table("Gender" = mht2$Gender, "mh_interview" = mht2$mental_health_interview)

f19 <- table("Gender" = mht2$Gender, "ph_interview" = mht2$self_employed)

f20 <- table("Gender" = mht2$Gender, "mental_vs_physical" = mht2$mental_vs_physical)

f21 <- table("Gender" = mht2$Gender, "obs_consequence" = mht2$obs_consequence)
```

## We'll first use Fisher's Test to see if there are some variables
## where there are differences in the survey results in respect to 
## the survey takers' gender.

```{r}
pairwiseNominalIndependence(f1, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f2, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f3, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f4, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f5, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3, simulate.p.value = T)[3, ]

pairwiseNominalIndependence(f6, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f7, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f8, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f9, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f10, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f11, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f12, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f13, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f14, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f15, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f16, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f17, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f18, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f19, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f20, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]

pairwiseNominalIndependence(f21, compare = "row", fisher = T,
gtest = F, chisq = F, digits = 3)[3, ]
```

```
Using the adjusted P-value of the results, we can see that the most
significant variables (using a threshold of 0.05) are:
family_history, treatment, work_interfere, no_employees, tech_company,
benefits, care_options, mental_health_consequence, phys_health_consequence,
supervisor, mental_health_interview, and obs_consequence.
```
## Let's see the confusion matrices for those that are significant.

```{r}
# We'll use proportion tables where the total amount of 
# the respective gender is used instead of the grand total
# to calculate the proportions.

list("family_history" = prop.table(f2[-1, ], margin = 1), 
     "Treatment" = prop.table(f3[-1, ],margin = 1), 
     "work_interfere" = prop.table(f4[-1, ], margin = 1), 
     "no_employees" = prop.table(f5[-1, ], margin = 1), 
     "tech_company" = prop.table(f7[-1, ], margin = 1), 
     "benefits" = prop.table(f8[-1, ], margin = 1), 
     "care_options" = prop.table(f9[-1, ], margin = 1), 
     "mental_health_consequence" = prop.table(f14[-1, ], margin = 1), 
     "phys_health_consequence" = prop.table(f15[-1, ], margin = 1), 
     "supervisor" = prop.table(f17[-1, ], margin = 1), 
     "mental_health_interview" = prop.table(f18[-1, ], margin = 1), 
     "obs_consequence" = prop.table(f21[-1, ], margin = 1))
```

```
We'll make some simple interpretations of the results we see above,
though there'll be some assumptions that'll be made:

family_history - Women are more likely to have/admit that they have
a family history of mental illness than men.

treatment: Women are more likely to admit/seek out treatments for
their mental health than men are.

work_interfere: More men claim to never have mental health issues
interfere with their work than women.However, the other answers
where there are some claims of interference have seemingly similar
rates between both genders, though women still are a bit more likely
to admit it.

no_employees: More men appear to work in smaller companies while
women appear to work in larger companies.

tech_company: More men in this survey work in tech companies than 
women, although the gap seems to be narrowing. 

benefits: More women seem to understand the mental health benefits
their employers offer than men. Perhaps women are more likely to 
care about/seek out information relating to benefits than men are.

care_options: Similarly to "benefits", women are more likely to
know and undersrtand their mental health care options their 
workplace offers than men are.

mental_health_consequence: More women believe that there's a possibility
that discussing mental health issues with their employers will lead to 
negative consequences than men. However, more men are confident that
talking about mental health issues won't lead to consequences than women.
It's unknown if this is because men just don't seem to care much for 
mental health issues, are confident in their abilities to get their 
employers on their side, or something else.

phys_health_consequence: Very similar to the results and interpretation
found in "mental_health_consequence".

supervisor: More men are likely to discuss mental health issues with their
direct supervisors tahn women are. However, more women are likely to be 
more selective about which supervisor to talk to compared to men acccording to
percent of answers for "Some of them".

mental_health_interview: Women are both far less unlikely to outright discuss
mental health issues in an interview and less likely to consider doing so than 
ment are. While 8% of women would consider bringing up the subject in an
interview, nearly 19% would consider doing so. It is unclear if this is 
because men are more confident in bringing up mental health issues in an
interview, women believe they'll be taken less seriously as a candidate, both,
or something else entirely.

obs_consequence: Slighltly more women claimed to have heard of or observed negative 
consequences for coworkers with mental health issues than men have.
```

# Is it possible to predict whether someone is male or female
# based on the results of the survey answers?

## We'll use Random Forest to see if this is possible.

```{r}
library(randomForest)
library(caret)
set.seed(11)
mht_mf <- mht2[-which(mht2$Gender == "Other"), ]
mht_mf$Gender <- droplevels(mht_mf$Gender, exclude = "Other")
mht_mf <- mht_mf[, -c(1, 5, 6, 27)] # Exclude filler variables

# We'll split 70/30
sbst <- createDataPartition(mht_mf$Gender, p = 0.7, list = F)
train1 <- mht_mf[sbst, ]
test1 <- mht_mf[-sbst, ]

# We now begin the random forest modeling
survey_rf <- randomForest(Gender ~ ., train1, mtry = 23, 
                       importance = T, na.action = na.omit)
# Using the model, we'll the testing eubset to make predictions.
survey_pred1 <- predict(survey_rf, test1)
varImpPlot(survey_rf)

# Oddly enough, state and age seems to have the most influence on
# predicting the genders of the survey takers.

table_survey1 <- table("original" = test1$Gender, "prediction" = survey_pred1)
table_survey1
accuracy <- sum(diag(table_survey1)) / sum(table_survey1)
accuracy # Calculation of the prediction accuracy.

# While the accuracy percentage itself looks impressive, looking
# at the table does not as the model has a poor time predicting
# which of the survey takers are female whereas it has an easier
# time predicting male survey takers.

# Let's see what happens when we only use the variables that
# were found to be significant in the Fisher's Tests.
mht_mf2 <- mht_mf[, -c(1, 3, 8, 12, 13, 14, 15, 18, 
                       21, 22, 24)]

# We'll split 70/30
sbst2 <- createDataPartition(mht_mf2$Gender, p = 0.5, list = F)
train2 <- mht_mf2[sbst2, ]
test2 <- mht_mf2[-sbst2, ]

# We now begin the random forest modeling
survey_rf2 <- randomForest(Gender ~ ., train2, mtry = 12, 
                       importance = T, na.action = na.omit)
# Using the model, we'll the testing eubset to make predictions.
survey_pred2 <- predict(survey_rf2, test2)
varImpPlot(survey_rf2)

table_survey2 <- table("original" = test2$Gender, "prediction" = survey_pred2)
table_survey2
accuracy2 <- sum(diag(table_survey2)) / sum(table_survey2)
accuracy2 # Calculation of the prediction accuracy.

# The second model gains slightly more accuracy predicting which 
# survey takers are female but loses some with predicting males.
# Overall, it's not very feasible to predict and distinguish between
# men and women using a model on the survey answers. However,
# this shouldn't discount the results gotten from the Fisher's Tests.
```

```
It's possible I may come back and continue analyzing this data set. Maybe next time,
I'll see if geography produces differences in survey results. Maybe I'll try to
optimize the random forest model and see if I squeeze out some more accuracy out of
the prediction rates for women. But for now. Ultimately, I just think that there wasn't 
enough of a sample size compared to men and secondly, the answers (yes even some
of those deemed significant by the Fisher's Tests) were mostly similar for both
genders. Granted, there are a few questions/variables where the answers were
night and day but I don't even think those variables alone could've helped out the model.
I'll definitely be moving onto a different data set for the meantime. Until next time...
```

